Efficiently summarising relationships in large samples: a general duality between statistics of genealogies and genomes

### 2019-09-03 treestats_paper.tex
Tweaked plot & added to paper.

\caption{
\label{fig:algorithm_example}
Illustration of the internal state for algorithm B for $\iw = \bone_S$ and
$f(x) = x(5 - x) / 20$ as in Example~\ref{ex:site_diversity}. (A)
Immediately before we remove the edge joining 6 to 7 and (B) immediately after.
See the text for descriptions of the arrays encoding the state.}
\end{figure}

@@

>>>>

\caption{
Illustration of the internal state for algorithm B for $\iw = \bone_S$ and
$f(x) = x(5 - x) / 20$ as in Example~\ref{ex:site_diversity}. (A)
Immediately before we remove the edge joining 6 to 7 and (B) immediately after.
See the text for descriptions of the arrays encoding the state.
\label{fig:algorithm_example}}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics{tskit_stat_benchmarks/benchmarks_without_copy_longer_genome.pdf}
    \caption{Comparison of time required to compute site statistics
        between matrix and tree based methods. [Details]
        \label{fig:stats_performance}
    }
\end{figure}
